---
title: "Psi Chi R - Mar 2025"
#date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---
Start Date: 7 Mar 2025

Report Date: `r format(Sys.Date(), '%d %B %Y')`

[Source: Psi Chi R](https://osf.io/vz3uj/wiki/home/)

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

#setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

rm(list=ls())

setwd("~/R/Psi_Chi_R")

library(tidyverse)

#total for bottom row
sum_rows = function(x) {
  x = as.data.frame(x)
  sums = sapply(x,function(col) if (is.numeric(col)) sum(col, na.rm = T) else NA)
  sums = as.data.frame(t(sums))
  names(sums) = names(x)
  rbind(x, sums)
}

## right column for total
sum_cols = function(x) {
  x$Total = rowSums(x[sapply(x, is.numeric)], na.rm = T)
  x
}

#dollar format function
dollars = function(x) {
  paste0("$",format(x,big.mark= ",",scientific=F))
}

desc_stats = function(x){
  c(min = min(x,na.rm=T),
    median = median(x,na.rm=T),
    max = max(x,na.rm=T),
    mean = mean(x,na.rm=T),
    sd = sd(x,na.rm=T))
}
```


## Clean and EDA
```{r}
data=read_csv('data.csv')

names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2) %>% 
  arrange(desc(Per_of_Missing))
```

## Level 1: Sort the data by GPA from low to high.

```{r}
data %>% 
  select(GPA,everything()) %>% 
  group_by(GPA) %>% 
  arrange(GPA) %>% 
  head()
```

Level 2: Produce the means and standard deviations for the following variables:
GPA

```{r}
level2_list = c()
desc_stats(data$GPA) %>% print()
```

Male_score (recognition for male psychologists like Sigmund Freud; higher scores = more recognition)

```{r}
desc_stats()
```

Female_score (recognition for psychologist women)

POC_score (recognition for psychologists of color)

White_score (recognition for white psychologists)

Level 3: Create a graph to compare the mean scores for recognition of women and for recognition of men.

Level 4: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable across male and female participants (Gender).

Level 4 Bonus: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable between people who have completed a history of psychology course and people who have not taken a history of psychology course (Taken_history).



```{r include=F}
#beep when done
if (require("beepr"))
  beepr::beep(2)
```