---
title: "Psi Chi R - August 2024"
author: "by Alan Lam"
#date: "`r Sys.Date()`"
date: "Date: `r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: kable
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R](https://osf.io/hmbxs/wiki/home/)

Happy August! This month we are using data from the Psi Chi NICE project: Understanding Family Dynamics in a Cross-Cultural Sample. The manuscript for this project, which was the first ever NICE project, was recently published.

You may access the prompts here. The data is available here.

The contest opens August 1 and closes (latest time zone on earth) August 31st 2024. The contest entry form is available here.

After the close of the contest, an answer key will be uploaded - please note that there are often multiple ways to arrive at the correct answer.

Please contact RAC member Dr. Kelly Cuccolo, kcuccolo@mivu.org with any questions. Note that Dr. Cuccolo will be on vacation and unreachable from August 5th to the 13th.

## Load packages and import data

```{r setup, warning=F,message=F}
#library(tidyverse)

library(dplyr)
#library(purrr)
library(ggplot2)

dataset=read.csv('https://osf.io/download/j58c7')

```

```{r}
#skimr::skim(dataset)
```

Codebook: https://osf.io/ey7ph

## Data processing (level 1)
Filter out participants who have progress values less than 100
```{r}
dataset1 = dataset %>% 
  filter(Progress < 100)
```

Filter out participants who are missing values for age and for gender. 

```{r}
dataset2 = dataset1 %>% 
  filter(!is.na(Age),
         !is.na(Gender))
```

## Descriptive Statistics (level 2)
Create a variable called FACEcomm (Family Communication) by adding together the following items FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52

oNote the average, standard deviation, and median values for the FACEcomm variable. 
```{r}
dataset3=dataset2 %>% 
  mutate(FACEcomm = FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52) %>% 
  select(FACEcomm,everything())
```

Find the range as well.

## Data visualization (level 3)
Create a box plot of the FACEcomm variable to identify any outliers

Create a histogram on the FACEcomm variable to help visualize the distribution 

## Inferential statistics (level 4)

If you identified outliers in the previous step, filter them out from the data.

Is there a significant difference in FACEcomm between people who identify with ‘Religionnow’ = 1 and ‘Religionnow’ = 11?

```{r}

```



```{r include=FALSE}
#beep when done
if (require("beepr",quietly = T))
  beepr::beep(2)
```
