---
title: "Psi Chi R - August 2024"
author: "by Alan Lam"
#date: "`r Sys.Date()`"
#date: "Date: `r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: kable
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---
Start Date: August 5, 2024

Report Date: `r format(Sys.Date(), '%d %B %Y')`

[**Source**: Psi Chi R](https://osf.io/hmbxs/wiki/home/)

Happy August! This month we are using data from the Psi Chi NICE project: Understanding Family Dynamics in a Cross-Cultural Sample. The manuscript for this project, which was the first ever NICE project, was recently published.

Codebook: https://osf.io/ey7ph

## Load packages and import data

```{r setup, warning=F,message=F}
#library(tidyverse)
#library(purr)

library(dplyr)
library(ggplot2)

dataset=read.csv('https://osf.io/download/j58c7')

```

```{r}
#skimr::skim(dataset)
```


## Data processing (level 1)
Filter out participants who have progress values less than 100
```{r}
dataset1 = dataset %>% 
  filter(Progress < 100)

slice_sample(dataset1,n=5)
```

Filter out participants who are missing values for age and for gender. 

```{r}
dataset2 = dataset1 %>% 
  filter(!is.na(Age),
         !is.na(Gender))

slice_sample(dataset2,n=5)
```

## Descriptive Statistics (level 2)
Create a variable called FACEcomm (Family Communication) by adding together the following items FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52

```{r}
dataset3=dataset2 %>% 
  mutate(FACEcomm = FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52) %>% 
  select(FACEcomm,everything())

#skimr::skim(dataset3$FACEcomm)
```

-Note the average, standard deviation, and median values for the FACEcomm variable. Find the range as well.
```{r}
desc_stat = function(x){
  c(mean = mean(x,na.rm = T),
  standard_dev = sd(x,na.rm = T),
  median = median(x,na.rm = T),
  range = range(x,na.rm = T))
}

desc_stat(dataset3$FACEcomm)
#mean:37.31, SD: 5.67, median: 38, range: 26 to 50
```

## Data visualization (level 3)
Create a box plot of the FACEcomm variable to identify any outliers

```{r}
dataset4=dataset3 %>% 
  filter(!is.na(FACEcomm))

boxplot(dataset4$FACEcomm)

dataset4 %>% 
  ggplot(aes(y=FACEcomm))+
  geom_boxplot()
```

Create a histogram on the FACEcomm variable to help visualize the distribution 

```{r}
hist(dataset4$FACEcomm)

dataset4 %>% 
  ggplot(aes(x=FACEcomm))+
  geom_histogram(binwidth = 5)

dataset4 %>% 
  ggplot(aes(x=FACEcomm))+
  geom_density()

```


## Inferential statistics (level 4)

If you identified outliers in the previous step, filter them out from the data.
```{r}
dataset5=dataset4 %>% 
  filter(FACEcomm >= 33,
         FACEcomm <= 40)

slice_sample(dataset4,n=5)
```

Is there a significant difference in FACEcomm between people who identify with ‘Religionnow’ = 1 and ‘Religionnow’ = 11?

```{r}
religion_1=dataset5 %>% 
  filter(Religionnow=='1') %>% 
  select(Religionnow,everything())

religion_11=dataset5 %>% 
  filter(Religionnow=='11') %>% 
  select(Religionnow,everything())

shapiro.test(religion_1$FACEcomm)

shapiro.test(religion_11$FACEcomm)

hist(religion_1$FACEcomm)

hist(religion_11$FACEcomm)
```

```{r}
#no significant difference
t.test(religion_1$FACEcomm,religion_11$FACEcomm)
```



```{r include=FALSE}
#beep when done
if (require("beepr",quietly = T))
  beepr::beep(2)
```
