---
title: "Psi Chi R - June 2024"
author: "Alan Lam"
#date: "`r Sys.Date()`"
date: "`r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    always_allow_html: yes
    df_print: kable
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R](https://osf.io/3h4ge/)

## Load packages and import data

```{r}
#library(tidyverse)

library(dplyr)
library(purrr)

dataset=read.csv('https://osf.io/download/c3bfs/')
```

## Check the data

```{r}
head(dataset)

#skimr::skim(dataset)
```

```{r}
sum(is.na(dataset))

sum(is.null(dataset))

sum(!complete.cases(dataset))
```

## Level 1

Let’s get familiar with our data. Create a table that shows the frequency of each type of Pokémon in the dataset (variable name: type1). 

```{r}
tab1 = dataset %>% 
  group_by(type1) %>% 
  count() %>% 
  arrange(desc(n))

tab1
```

Next, let’s look at the representation of each generation of Pokémon in the dataset. Create a table that shows the number of Pokémon in the dataset associated with each generation (variable name: generation)
```{r}
tab2 = dataset %>% 
  group_by(generation) %>% 
  count() %>% 
  arrange(desc(n))

tab2
```


## Level 2-

Provide the mean, standard deviation, median, and range of values of attack stats (variable name: attack) for ‘Water’ type Pokémon (variable name: type1). 

```{r}
water_attack = dataset %>% 
  filter(type1 == 'Water') %>% 
  select(attack)

#create function for desc stats
desc_stat = function(x){
  list(mean = mean(x,na.rm = T),
  standard_dev = sd(x,na.rm = T),
  median = median(x,na.rm = T),
  range = range(x,na.rm = T))
}

map(water_attack,desc_stat)
  
```

-Provide the mean, standard deviation, median, and range of values of speed stats (variable name: speed) for ‘Dragon’ type Pokémon (variable name: type1). 

```{r}
dragon_speed = dataset %>% 
  filter(type1 == 'Dragon') %>% 
  select(speed)

map(dragon_speed,desc_stat)


```

## Level 3-

Are there any outliers for the ‘total’ stat? What is the value(s), and which Pokémon(s) is/are associated with it?
```{r}
library(ggplot2)

boxplot(dataset$total)

dataset %>% 
  ggplot(aes(x=total))+
  geom_bar()

```

##Level 4-

Is there a correlation between a Pokémon’s ‘total’ stat and their base level of experience? (variable: base_exp)-Create a visualization that shows the average ‘total’ stat based on the primary type of the Pokémon (type1)

```{r}
dataset2=dataset %>% 
  mutate(base_exp2=as.numeric(base_exp)) %>% 
  filter(complete.cases(base_exp2))

cor.test(dataset2$total,dataset2$base_exp2)

```

```{r}
cor_data = dataset2[,c(18,30)] %>% 
  tibble()

cor_matrix= cor_data %>% 
  cor() %>% 
  round(digits = 2) %>% 
  as.data.frame()

plot(cor_data)
```

