---
title: "Psi Chi R - Feb 2025"
#date: "`r Sys.Date()`"
#date: "Date: `r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---


https://osf.io/by4hr/wiki/home/

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

#setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

rm(list=ls())

setwd("~/R/Psi_Chi_R")

library(tidyverse)

#total for bottom row
sum_rows = function(x) {
  x = as.data.frame(x)
  sums = sapply(x,function(col) if (is.numeric(col)) sum(col, na.rm = T) else NA)
  sums = as.data.frame(t(sums))
  names(sums) = names(x)
  rbind(x, sums)
}

## right column for total
sum_cols = function(x) {
  x$Total = rowSums(x[sapply(x, is.numeric)], na.rm = T)
  x
}

#dollar format function
dollars = function(x) {
  paste0("$",format(x,big.mark= ",",scientific=F))
}

desc_stats = function(x){
  c(min = min(x,na.rm=T),
    mode = mode(x,na.rm=T),
    median = median(x,na.rm=T),
    max = max(x,na.rm=T),
    mean = mean(x,na.rm=T),
    sd = sd(x,na.rm=T))
}

#remove upper outliers
upper_fence = function(x){
  quantile(x,.75) + (1.5*IQR(x))
}

#remove lower outliers
lower_fence = function(x){
  quantile(x,.25) - (1.5*IQR(x))
}
```

## Clean and EDA
```{r}
data=read_csv('data.csv')

names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2) %>% 
  arrange(-Per_of_Missing)
```

# Your tasks for the PsiChiR contest for Feb. 2025 include:

## Level 1: Remove participants outside of the United States AND participants who are not identified as "white" (white participants are coded as "1" for the variable "Race").

```{r}
data1 = data %>% 
  filter(VGeoCountry == 'United States',
         Race == '1') %>% 
  tibble()

```


## Level 2: For the remaining participants, calculate the percentage of participants who fell into each income category (1 through 5).

```{r}
data1_table = data1 %>% 
  mutate(Income = as.character(Income)) %>% 
  group_by(Income) %>% 
  summarise(headcount = n()) %>% 
  mutate(percent = headcount/sum(headcount,na.rm = T) * 100) %>%   arrange(desc(percent)) %>% 
  sum_rows() %>% 
  mutate(percent = paste(round(percent,2),"%"))

print(data1_table)
```

## Level 3: Create a graph (such as a bar graph) that displays the M and SD for "General Support for Affirmative Action" (variable = "AA") across income groups.

```{r}
#M for median
data1.5 = data1 %>% 
  group_by(Income) %>% 
  summarise(Mean = mean(AA,na.rm = T),
            Median = median(AA,na.rm=T),
            SD = sd(AA,na.rm=T))

data1.5 %>% 
  ggplot(aes(x=Income,y=Median))+
  geom_col(fill='darkblue')+
  theme_bw()+
  labs(title='Median of AA by Income')+
  theme(plot.title = element_text(hjust = .5))

data1.5 %>% 
  ggplot(aes(x=Income,y=SD))+
  geom_col(fill='darkred')+
  theme_bw()+
  labs(title='Stand Deviation of AA by Income')+
  theme(plot.title = element_text(hjust = .5))
```


## Level 4: Test whether "General Support for Affirmative Action" (variable = "AA") differs across income group.

```{r}
data1 %>% 
  ggplot(aes(x=Income,y=AA))+
  geom_col(fill='darkgreen')+
  theme_bw()+
  labs(x='Income Group',y='Affirmative Action Support',title="Affirmative Action Across the Income-verse")+
  theme(plot.title = element_text(hjust = .5))
```

```{r}
#non-normality
shapiro.test(data1$Income)
shapiro.test(data1$AA)

hist(data1$Income)
hist(data1$AA)
```

```{r}
#yes, support for AA differs among income group
wilcox.test(data1$Income,data1$AA)
```

## Extra Misc.

```{r}
cor(data1$Age,select_if(data1,is.numeric))

cor.test(data1$Age,data1$AA)

qqnorm(data1$Age)

qqnorm(data1$AA)

qqplot(data1$Age,data1$AA)

data1 %>% 
  ggplot(aes(Age,AA))+
  geom_col()
```

```{r}
library(tidymodels)

data1_split = initial_split(data1,prop=.75)

data1_test = testing(data1_split)

data1_train = training(data1_split)
```


```{r}
data1_train %>% 
  ggplot(aes(Age,AA))+
  geom_point()

model = fit(object = linear_reg(),formula = Age ~ AA,data=data1_train)

tidy(model)
```

```{r}
model_results = data1_test %>% 
  mutate(predict(model,new_data = data1_test))

model_results %>% 
  ggplot()+
  theme_bw()+
  geom_point(aes(x=Age,y=AA))+
  geom_point(aes(x=Age,y=.pred),col='red')
```


```{r include=F}
#beep when done
if (require("beepr"))
  beepr::beep(2)
```
