---
title: "Psi Chi R - Jan 2025"
#date: "`r Sys.Date()`"
#date: "Date: `r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

Hello! Welcome to January's contest. In honor of National Cheese Day (January 20th) we'll be looking into some award winning cheeses! This month, we'll also test out learning a new skill (for you, and ME!) - making maps! One of the tasks for this month will be to map out winning cheeses. Please note, this is one of my first attempts at making maps in R so it is not by any means fancy, but, I feel it is important for all of us to try learning new things :)

https://osf.io/2hgzs/wiki/home/

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

#setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

setwd("~/R/Psi_Chi_R")

library(tidyverse)

data=read_csv('data.csv')

sum_rows = function(x){
  x %>% 
    ungroup() %>% 
    bind_rows(summarise(.,across(where(is.numeric),sum,na.rm=T)))
}

sum_cols = function(x){
  x %>% 
    mutate(Total = rowSums(across(where(is.numeric)), na.rm =T))
}

```

## #EDA
```{r}
names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2)
```

## Level 1.

Remove any rows where ‘company,’ ‘product_name,’ and/or ‘rating’ are blank.

```{r}
data1 = data %>% 
  filter(!is.na(company),
         !is.na(product_name),
         !is.na(rating))
```


## Level 2.

Make one table that shows the counts of each category within ‘rating,’ and then make a second table showing counts for each ‘country.’

```{r}
data1 %>% 
  group_by(rating) %>% 
  count() %>% 
  arrange(desc(n))

data1 %>% 
  group_by(country) %>% 
  count() %>% 
  arrange(desc(n))
```

## Level 3.
First, make a table showing how many of each medal type (rating) each cheese (Category_Corrected).

```{r}
data1 %>% 
  group_by(rating,Category.Corrected)
```

Which cheese has the most “Super Golds?” Next, modify the table and indicate which country produced the most “Super Gold” cheeses.

5004 - Hard goats' milk cheese plain
Spain
```{r}
data1 %>% 
  group_by(Category.Corrected,rating,country) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  filter(rating=='SUPER GOLD')
```

## Level 4.
Generate a map that shows which countries have won super gold medals. Since this is a more advanced skill, I’ve provided a starter code below
```{r}
data1 %>% 
  filter(rating=='SUPER GOLD') %>% 
  ggplot(aes(y=(fct_infreq(country))))+
  geom_bar()+
  labs(x='Super Gold Medals',
       title='Super Gold Medals by Country')+
  theme(plot.title = element_text(hjust = .5))
```


```{r}

```

