---
title: "Psi Chi R - July 2024"
author: "by Alan Lam"
#date: "`r Sys.Date()`"
date: "Date: `r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: kable
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R](https://osf.io/4pbuc/)

## Load packages and import data

```{r setup, warning=F,message=F}
#library(tidyverse)

library(dplyr)
#library(purrr)
library(ggplot2)

dataset=read.csv('https://osf.io/download/xq8us/')
```

```{r}
skimr::skim(dataset)
```

## Level 1 

-Let’s get familiar with our data. Create a table that shows the frequency of each Country in the dataset. 

```{r}
tab1 =dataset %>% 
  group_by(Country_Name) %>% 
  summarise(Frequency=n())

slice_sample(tab1,n=5)
```

## Level 2

-Next, let’s look at the representation of each country’s medal status. Create atable that shows the number of times each country has won a bronze, silver, and gold medal.

```{r}
tab2=dataset %>% 
  group_by(Country_Name) %>% 
  summarise(Gold = sum(Gold), Silver = sum(Silver), Bronze = sum(Bronze))

slice_sample(tab2,n=5)
```

## Level 3

-Is there a difference in the number of silver medals a country earns if they are competing in their home country? *Note please pick any one country you’d like to look at

```{r}
home=dataset %>% 
  filter(Host_country=='United States') %>% 
  group_by(Country_Name) %>% 
  summarise(Silver = sum(Silver)) %>% 
  mutate(Percent_Win = round(Silver/sum(Silver) * 100,2))

away =dataset %>%
  filter(!Host_country=='United States') %>% 
  group_by(Country_Name) %>% 
  summarise(Silver = sum(Silver)) %>% 
  mutate(Percent_Win = round(Silver/sum(Silver) * 100,2))
```

```{r}
shapiro.test(home$Silver)
shapiro.test(away$Silver)

hist(home$Silver)
hist(away$Silver)
```


```{r}
wilcox1=wilcox.test(home$Silver,away$Silver)

#yes, there's a difference in the number of silver medals a country earns if they are competing in their home country
print(wilcox1)

```

## Level 4

-Create a visualization that shows the United State’s gold medal over time. 
```{r}

USA_visual = dataset %>% 
  filter(Country_Name == 'United States')

USA_visual %>% 
  ggplot(aes(x=Year,y=Gold))+
  geom_line(lwd=1,col='darkred')+
  theme_bw()+
  labs(y='Number of Gold Medals',
       x= 'Years',
       title = 'The Roller Coaster of the American Quest for Gold',
       subtitle = "Examining the trajectory of the fight for the ultimate prize",fill=' ')+
  theme(plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))
```

```{r include=FALSE}
#beep when done
if (require("beepr",quietly = T))
  beepr::beep(2)
```