---
title: "Psi Chi R Contest - August 2023"
output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    code_folding: hide
---
[**Source**: Psi Chi R Contest - August](https://osf.io/jbn6a/wiki/home/)

The Psi Chi R Contests are a great way to practice base R. Click **Source** for more info.



## Data processing (level 1)

```{r setup,include=F}
#**Code will be revealed after the submission deadline.**
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```
Write a script that will filter out participants who are missing values for the age variable
```{r}
#Write a script that will filter out participants who are missing values for the age variable
august=read.csv('Aug_R_Contest.csv')

missing_age= subset(august,complete.cases(Age))

head(missing_age)

write.csv(missing_age,file='see.csv')
```

## Descriptive Statistics (level 2)
Create a variable called FACEcomm (Family Communication) by adding together the following items FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52
```{r}
#Create a variable called FACEcomm (Family Communication) by adding together the following items FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52

missing_age$FACEcomm=missing_age$FACES43 + missing_age$FACES44 + missing_age$FACES45 + missing_age$FACES46 + missing_age$FACES47 + missing_age$FACES48 + missing_age$FACES49 + missing_age$FACES50 + missing_age$FACES51 + missing_age$FACES52

```
Note the average, standard deviation, and median values for the FACEcomm variable.
Create a variable called SSBQtotal (Total Safe Sex Behavior) through two steps:

Reverse Score SBQ2 INTO SBQ2R, SBQ7 INTO SBQ7R, SBQ8 INTO SBQ8R, SBQ14 INTO SBQ14R, SBQ16 INTO SBQ16R, SBQ17 INTO SBQ17R, SBQ22 INTO SBQ22R, SBQ24 INTO SBQ24R, SBQ25 INTO SBQ25R (1 = Always 2 = Most of the time 3 = Sometimes 4 = Never)

Add the following items together: SBQ1 + SBQ2R + SBQ3 + SBQ4 + SBQ5 + SBQ6 + SBQ7R + SBQ8R + SBQ9 + SBQ10 + SBQ11 + SBQ12 + SBQ13 + SBQ14R + SBQ15 + SBQ16R + SBQ17R + SBQ18 + SBQ19 + SBQ20 + SBQ21 + SBQ22R + SBQ23 + SBQ24R + SBQ25R

Note the average, standard deviation, and median values for the SSBQtotal variable
```{r}
#Note the average, standard deviation, and median values for the FACEcomm variable.

mean_face=mean(missing_age$FACEcomm,na.rm=T)
sd_face=sd(missing_age$FACEcomm,na.rm=T)
median_face=median(missing_age$FACEcomm,na.rm=T)

print(mean_face)
print(sd_face)
print(median_face)

#Create a variable called SSBQtotal (Total Safe Sex Behavior) through two steps:


#Reverse Score SBQ2 INTO SBQ2R, SBQ7 INTO SBQ7R, SBQ8 INTO SBQ8R, SBQ14 INTO SBQ14R, SBQ16 INTO SBQ16R, SBQ17 INTO SBQ17R, SBQ22 INTO SBQ22R, SBQ24 INTO SBQ24R, SBQ25 INTO SBQ25R (1 = Always 2 = Most of the time 3 = Sometimes 4 = Never)
missing_age$SBQ2R =5 - missing_age$SBQ2
missing_age$SBQ7R =5 - missing_age$SBQ7
missing_age$SBQ8R =5 - missing_age$SBQ8
missing_age$SBQ14R =5 - missing_age$SBQ14
missing_age$SBQ16R =5 - missing_age$SBQ16
missing_age$SBQ17R =5 - missing_age$SBQ17
missing_age$SBQ22R =5 - missing_age$SBQ22
missing_age$SBQ24R =5 - missing_age$SBQ24
missing_age$SBQ25R =5 - missing_age$SBQ25

#Add the following items together: SBQ1 + SBQ2R + SBQ3 + SBQ4 + SBQ5 + SBQ6 + SBQ7R + SBQ8R + SBQ9 + SBQ10 + SBQ11 + SBQ12 + SBQ13 + SBQ14R + SBQ15 + SBQ16R + SBQ17R + SBQ18 + SBQ19 + SBQ20 + SBQ21 + SBQ22R + SBQ23 + SBQ24R + SBQ25R
missing_age$SSBQtotal=(missing_age$SBQ1 + missing_age$SBQ2R + missing_age$SBQ3 + missing_age$SBQ4 + missing_age$SBQ5 + missing_age$SBQ6 + missing_age$SBQ7R + missing_age$SBQ8R + missing_age$SBQ9 + missing_age$SBQ10 + missing_age$SBQ11 + missing_age$SBQ12 + missing_age$SBQ13 + missing_age$SBQ14R + missing_age$SBQ15 + missing_age$SBQ16R + missing_age$SBQ17R + missing_age$SBQ18 + missing_age$SBQ19 + missing_age$SBQ20 + missing_age$SBQ21 + missing_age$SBQ22R + missing_age$SBQ23 + missing_age$SBQ24R + missing_age$SBQ25R)

#Note the average, standard deviation, and median values for the SSBQtotal variable
mean1=mean(missing_age$SSBQtotal,na.rm=T)
sd1=sd(missing_age$SSBQtotal,na.rm=T)
median1=median(missing_age$SSBQtotal,na.rm=T)

print(mean1)
print(sd1)
print(median1)
```

## Data visualization (level 3)
Create a bar graph that shows the mean levels of FACEcomm and SSBQtotal
```{r}
#Create a bar graph that shows the mean levels of FACEcomm and SSBQtotal
mean_facecomm=mean(missing_age$FACEcomm,na.rm=T)
mean_ssbqtotal=mean(missing_age$SSBQtotal,na.rm=T)

barplot(c(mean_facecomm,mean_ssbqtotal),names.arg=c('Family Communication','Total Safe Sex Behavior'),ylab = 'Mean', main ='Comparing Family Communication and Total Safe Sex Behavior')

```

## Inferential statistics (level 4)
Test if there is an association between total safe sex behavior (SSBQtotal) and family communication (FACEcomm).
```{r}
#Test if there is an association between total safe sex behavior (SSBQtotal) and family communication (FACEcomm).

test_cor=cor(missing_age$FACEcomm,missing_age$SSBQtotal,use='pairwise.complete.obs')

print(test_cor)
```

```{r}
#Scatter plot
plot(missing_age$FACEcomm,missing_age$SSBQtotal,main='Between safe sex and family communication',xlab='Family Communication',ylab='Total Safe Sex Behavior')

abline(lm(missing_age$SSBQtotal~missing_age$FACEcomm),col='red',lwd=2)
```
