---
title: "Psi Chi R Contest - Mar 2024"
author: "Alan Lam"
date: "2024-03-03"
output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R Contest](https://osf.io/k6efc/)


```{r setup,include=F}
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```

## Load packages
```{r}
#Load packages and import data

library(ggplot2)
library(dplyr)
library(skimr)

mar2024=read.csv('psichiR_mar2024.csv')
```

## Check data
```{r}
skimr::skim(mar2024)
```


## Level 1 
-Let’s get familiar with our data. Create a table that shows how many times each genre is represented in the Top 50 most popular songs on Spotify. What is the most popular genre?

- Create a table that shows how many times each genre is represented in the Top 50 most popular songs on Spotify. What is the most popular genre?
```{r}
mar2024 %>% 
  group_by(main_genre) %>% 
  summarise(Count=n()) %>% 
  arrange(-Count) #Pop
```

-Which artist, if any, has the greatest number of Top 50 most popular songs on Spotify?
```{r}
mar2024 %>% 
  group_by(artist_name) %>% 
  summarise(Count=n()) %>% 
  arrange(-Count) #The Weeknd
```

## Level 2
-Provide the mean, standard deviation, median, and range of values for ‘danceability’
```{r}
summary(mar2024$danceability,na.rm=T)

mean(mar2024$danceability,na.rm = T) 
sd(mar2024$danceability,na.rm = T)
median(mar2024$danceability,na.rm = T)
range(mar2024$danceability,na.rm = T)
```

-Provide the mean, standard deviation, median, and range of values for ‘valence’
```{r}
summary(mar2024$valence,na.rm=T)

mean(mar2024$valence,na.rm = T)
sd(mar2024$valence,na.rm = T)
median(mar2024$valence,na.rm = T)
range(mar2024$valence,na.rm = T)

#Mean: 0.51, standard deviation: 0.21, median: 0.51, range: 0.13 - 0.89
```

-Provide the mean, standard deviation, median, and range of values for ‘energy’
```{r}
summary(mar2024$energy,na.rm=T)

mean(mar2024$energy,na.rm = T)
sd(mar2024$energy,na.rm = T)
median(mar2024$energy,na.rm = T)
range(mar2024$energy,na.rm = T)

#Mean: 0.66, standard deviation: 0.12, median: 0.12, range: 0.42 - 0.97
```


## Level 3
-Does the ‘tempo’ variable meet the assumption of normality?

```{r}
shapiro.test(mar2024$tempo)

hist(mar2024$tempo,freq=F,breaks = 15)
lines(density(mar2024$tempo),col='red',lwd=2)#Yes, 'tempo' meets normality.

```

## Using ggplot to imitate base R
```{r}
mar2024 %>% 
  ggplot(aes(x=tempo))+
  geom_histogram(aes(y=..density..),bins = 15,col='black',fill='lightgray')+
  geom_density(col='red',lwd=2)+
  theme_classic()+
  labs(title='Histogram of mar2024$tempo')+
  theme(plot.title = element_text(hjust = .5))

```

-Produce a visual that will show if the ‘loudness’ variable contains any outliers.

```{r}
plot(mar2024$loudness)
hist(mar2024$loudness)
```

-Is there a significant difference in the ratings of ‘danceability’ for explicit songs, compared to songs that are not explicit? Note all key statistics.

## Create DFs
```{r}
explicit_dance=mar2024 %>% 
  filter(is_explicit==TRUE)

explicit.not_dance=mar2024 %>% 
  filter(is_explicit==FALSE)
```

## Test for normality
```{r}
shapiro.test(explicit.not_dance$danceability)
shapiro.test(explicit_dance$danceability) #p-val. below 0.05, so assume normality

hist(explicit.not_dance$danceability,freq=F)
lines(density(explicit.not_dance$danceability))

hist(explicit_dance$danceability,freq=F)
lines(density(explicit_dance$danceability))
```

## Run t-test
```{r}
t.test(explicit.not_dance$danceability,explicit_dance$danceability) #No, there is no significant difference between non-explicit and explicit for 'danceability.'

```

## Level 4
-Create a regression model to figure out which of the following is the strongest predictor of popularity: danceability, valence, energy, loudness, acousticness. Instrumentalness, liveness, speechiness, or tempo. Please note all key statistics for each variable. 

```{r}
reg_model = lm(popularity ~ danceability + valence + energy + loudness + acousticness + instrumentalness + liveness + speechiness + tempo, data = mar2024)

plot(reg_model)

summary(reg_model) #Pr(>|t|) for danceability: 0.0761, valence: 0.4283, energy: 0.5354, loudness: 0.5659, acousticness: 0.1489, instrumentalness: 0.4737, liveness: 0.4424, speechiness: 0.4818, tempo: 0.8153 
```
--Didn't submit this part to the Psi Chi contest

## Plots for Model
```{r}
library(purrr)
library(ggplot2)

#Create list of variables to plot
plot_list = c('danceability','valence','energy','loudness','acousticness','instrumentalness','liveness','speechiness','tempo')

# Function create plots for each variable
plot_map = function(some_x) {
  ggplot(mar2024,aes(x = !!sym(some_x), y = popularity))+
    geom_point(aes(color = popularity), alpha = 0.5)+
    labs(title = paste0("Popularity and ", some_x), x = some_x, y = "Popularity")+
    geom_smooth(method = lm, se = FALSE)+
    theme_bw()+
    theme(plot.title = element_text(hjust = .5))
}

# list,function
map(plot_list, plot_map)

```


