---
title: "Psi Chi R Contest - Oct 2023"
author: "By Alan Lam"
output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: FALSE
---
[**Source**: Psi Chi R Contest](https://osf.io/2ac4b/wiki/home/)

**Code will be revealed after the submission deadline.**

```{r setup,include=F,echo=F}
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```

```{r}
#Load packages and import data

library(ggplot2)
library(dplyr)
library(lubridate)
library(readr)

october=read.csv('october_psichiR_movies.csv')
```


## Data processing (level 1)

1.    Write a script that will filter out movies that are missing a value in the ‘Budget’ column.

```{r}
octBudget=october %>% 
  subset(!is.na(Budget))

```

2.    Write a script that will filter out movies that are missing a value in the ‘RunTime’ column.

```{r}
octRunTimeNA =octBudget%>% 
  subset(!is.na(RunTime))
```

## Descriptive Statistics (level 2)

3.    Write a script that will provide the average, standard deviation, median, and range of the ‘RunTime’ variable. Note the values you got.

```{r}
oct_descriptive= summary(octRunTimeNA$RunTime)

print(oct_descriptive)
sd(oct_descriptive)
range(oct_descriptive)

#Mean = 90.3, STD = 40.84176, Median = 90, Range = 45 to 170
```

4.    Write a script that will provide the average, standard deviation, median, and range of the ‘Budget’ variable. Note the values you got.

```{r}
oct_budget_description= summary(octRunTimeNA$Budget)

print(oct_budget_description)
sd(oct_budget_description)
range(oct_budget_description)

#Mean = 3828124, STD = 28022369, Median = 500000, Range = 100 to 70000000
```

5.    Write a script that will provide the average, standard deviation, median, and range of the ‘Review’ variable. Note the values you got from running the code.

```{r}
oct_review_description = summary(octRunTimeNA$Review)

print(oct_review_description)
sd(oct_review_description)
range(oct_review_description)

#Mean = 4.955, STD = 6.200773, Median = 4.9, Range = 1 - 20
```

## Data visualization (level 3)

6.    Create a graph that shows the ‘Budget’ for the movies in the dataset over time.

```{r}
#Transform dates

octRunTimeNA$Date=mdy(octRunTimeNA$Release_Date)

octRunTimeNA=octRunTimeNA %>% 
  select(Release_Date,Date,everything())

range(octRunTimeNA$Date) #Shows 1905 to 2017
```

```{r}
octRunTimeNA %>% 
  ggplot(aes(y=Budget,x=Date))+
  geom_line(col='darkgreen')+
  geom_point()+
  labs(title='Movie Budget Over the Years',subtitle="From 1905 to 2017",y=' ',x='Years')+
  theme_bw()+
  theme(plot.title = element_text(hjust=.5),plot.subtitle = element_text(hjust=.5))+
  scale_y_continuous(labels=scales::dollar_format())+
  expand_limits(y=80000000)
```

## Inferential statistics (level 4)

7.    Test if there are any associations between the following variables: ‘Review’, ‘Budget’, and ‘RunTime’. Note the key statistics you got from running the code.

```{r}
shapiro.test(octRunTimeNA$Review)
shapiro.test(octRunTimeNA$Budget)
shapiro.test(octRunTimeNA$RunTime)

cor.test(octRunTimeNA$Review,octRunTimeNA$Budget,method='spearman')
#p-value = 0.5632, rho 0.02132607 

cor.test(octRunTimeNA$Review,octRunTimeNA$RunTime,method='spearman')
#p-value = 0.00000006181, rho 0.1977713 

cor.test(octRunTimeNA$Budget,octRunTimeNA$RunTime,method='spearman')
#p-value < 2.2e-16, rho 0.3279512 

```
