---
title: "Psi Chi R - December 2024"
author: "by Alan Lam"
#date: "`r Sys.Date()`"
#date: "Date: `r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

Start Date: 7 Dec 2024

Report Date: `r format(Sys.Date(), '%d %B %Y')`

[**Source**: Psi Chi R](https://osf.io/ebkcj/)

Welcome to the contest for December! The prompts can be found here, and the data is available here. The contest will run until the last day of December (December 31st), latest time zone on earth.

```{r setup, warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

library(tidyverse)

data=read_csv('data.csv')

#access CSV directly through URL; local copy will be overwritten with a different month's data

#data= read.csv('https://osf.io/download/7uc9x/')
```

## Skim and clean
```{r}
## EDA

names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2)

```


## Level 1: 
Write a script that will remove participants who are missing the ‘age’ variable. Then, write a script that will show the distribution of the ‘rating’ variable. Is ‘Review Rating’ skewed?

```{r}
data1 = data %>% 
  filter(!is.na(Age))

hist(data1$Review.Rating)
boxplot(data1$Review.Rating)
shapiro.test(data1$Review.Rating)

#yes, Review Rating is skewed.
```

## Level 2: 
Find the min, median, max, average, and standard deviation of ‘Review Rating’

```{r}
desc_stats = function(x) {
            c(min = min(x,na.rm = T),
              median = median(x,na.rm=T),
              max = max(x,na.rm = T),
              average = mean(x,na.rm=T),
              standard_dev = sd(x,na.rm=T))
}

print(desc_stats(data1$Review.Rating))
```

## Level 3: 
Create a table that shows the average ‘Review Rating’ for each ‘Category.'

```{r}
review_rating_table = data1 %>% 
  group_by(Category) %>% 
  summarise(Average_Review_Rating = mean(Review.Rating,na.rm = T))

print(review_rating_table)
```

## Level 4: 
Create a visualization showing the relationship between ‘Purchase Amount (USD)’ and ‘Review Rating.’ 

```{r}

data1 %>% 
  ggplot(aes(x=Review.Rating,y=Purchase.Amount..USD.))+
  geom_point()+
  geom_smooth(method = "lm", se = T) 


```

Test the correlation between the variables. What is the rvalue? What is the p value?
```{r}
shapiro.test(data1$Purchase.Amount..USD.)

shapiro.test(data1$Review.Rating)

cor.test(data1$Purchase.Amount..USD.,data1$Review.Rating,method = 'spearman')
#p-value = 0.06224 and rho = 0.02994088
```



```{r include=FALSE}
#beep when done
if (require("beepr",quietly = T))
  beepr::beep(2)
```

