---
title: "Psi Chi R - Mar 2025"
#date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

Start Date: 4 April 2025

Report Date: `r format(Sys.Date(), '%d %B %Y')`

[Source: Psi Chi R](https://osf.io/jah5y/wiki/home/)

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

#setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

rm(list=ls())

setwd("~/R/Psi_Chi_R")

library(tidyverse)

#total for bottom row
sum_rows = function(x) {
  x = as.data.frame(x)
  sums = sapply(x,function(col) if (is.numeric(col)) sum(col, na.rm = T) else NA)
  sums = as.data.frame(t(sums))
  names(sums) = names(x)
  rbind(x, sums)
}

## right column for total
sum_cols = function(x) {
  x$Total = rowSums(x[sapply(x, is.numeric)], na.rm = T)
  x
}

#dollar format function
dollars = function(x) {
  paste0("$",format(x,big.mark= ",",scientific=F))
}

desc_stats = function(x){
  c(min = min(x,na.rm=T),
    median = median(x,na.rm=T),
    max = max(x,na.rm=T),
    mean = mean(x,na.rm=T),
    sd = sd(x,na.rm=T))
}

#numeric notations
options(scipen=9999)
```

## Clean and EDA

```{r}
data=read_csv('data.csv')

names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2) %>% 
  arrange(desc(Per_of_Missing))
```

## Level 1: Let’s examine the average rating column for normality and outliers. Create a histogram, boxplot, and Q-Q plot. Please paste your graphs into the code/output you provide. Finally, run a Shapiro-Wilks test. Is the data normally distributed? Are there any outliers? 

```{r}

```


Level 2: Taking into consideration both average rating AND the number of ratings a book has received, what are the top five most popular books?

Level 3: Is there any relationship between when a book was published and its average ratings? 

Level 4: Pick your favorite author (or any author of your choosing) in the dataset and plot the relationship between the number of ratings they receive (column J) and the average ratings for their book (column D). What kind of relationship do you see, if any?


### Data set:

```{r echo=F}
downloadthis::download_this(data,output_name = '2025Apr_data',output_extension = '.xlsx')
```

```{r include=F}
#beep when done
if (require("beepr"))
  beepr::beep(2)
```