---
title: 'Psi Chi R Contest - Dec 2023'
author: 'By Alan Lam'
output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R Contest](https://osf.io/r86p2/)


```{r setup,include=F}
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```

```{r}
#Load packages and import data

#install.packages(ggplot2,dplyr,lubridate,readr)

library(ggplot2)
library(dplyr)
library(readr)

theme_set(theme_bw())

december=read.csv('C:/Users/alanh/Documents/R/Flight Data December 2023 Contest.csv')
```


## Level 1-
Provide descriptive statistics for the actual_flown_miles variable. Indicate the **minimum** number of miles flow, the **maximum** number of miles flow, the **average** number of miles flown, and the **median** number of miles flown.

```{r}
sum(is.na(december$actual_flown_miles))

min(december$actual_flown_miles,na.rm = T) #Minimum = 45

max(december$actual_flown_miles,na.rm=T) #Maximum = 8440

mean(december$actual_flown_miles,na.rm=T) #Average = 2477.738

median(december$actual_flown_miles,na.rm=T) #Median = 1846
```

## Level 2-
Describe the relationship between satisfaction (satisfaction_score) and delay time (arrival_delay_minutes). Note that for satisfaction_score a value of 1 is the lowest (dissatisfied) and 5 is the highest (satisfied). Note that negative values in the arrival delay minutes mean the flight was early, while positive values indicate the flight was late. 

```{r}
summary(december$satisfaction_score) #transform from char into numeric
summary(december$arrival_delay_minutes)

december$satisfaction_score=as.numeric(december$satisfaction_score)

december$arrival_delay_minutes=as.numeric(december$arrival_delay_minutes)

december1=december %>% 
  filter(complete.cases(satisfaction_score))

december2=december1 %>% 
  filter(complete.cases(arrival_delay_minutes))

cor.test(december2$satisfaction_score,december2$arrival_delay_minutes) #p-value < 2.2e-16, cor -0.07935616
```

## Level 3-
Does satisfaction level (satisfaction_score) vary by the cabin (cabin_code) that they’re in? 

```{r}
summary(december2$satisfaction_score)

december2 %>% 
  ggplot(aes(x=cabin_code,y=satisfaction_score,fill=satisfaction_type))+
  geom_col()+
  labs(title='Satisfaction Score by Cabin Type',y='Satisfaction Score',x='Cabin Type',fill='Satisfaction Type')+
  theme(plot.title = element_text(hjust=.5))

#Yes. Per the column chart, there are varying levels of satisfaction by cabin type.
```


## Level 4-

Describe the relationship between loyalty program membership (loyalty_program_level) and satisfaction (satisfaction_score). Hint: you’ll have to do some recoding for folks who don’t belong to a program

```{r}
december3=december2 %>% 
  filter(complete.cases(loyalty_program_level))

#Rename blanks as NA
december3$loyalty_program_level[december3$loyalty_program_level==""]="Non-Membership"

december3 %>% 
  ggplot(aes(y=loyalty_program_level,x=satisfaction_score,fill=satisfaction_type))+
  geom_col()+
  labs(title='Loyalty and Satisfaction',y='Program Membership',x='Satisfaction Score',fill='Satisfaction Type')+
  theme(plot.title = element_text(hjust=.5))

```


