---
title: "Psi Chi R Contest - Apr 2024"
author: "Alan Lam"
#date: "`r Sys.Date()`"
date: "`r format(Sys.Date(), '%d %B, %Y')`" 

output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R Contest](https://osf.io/vt4we/)

```{r setup,include=F}
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```

## Load packages and import data
```{r}

#library(tidyverse)

library(dplyr)
library(purrr)

dataset=read.csv('https://osf.io/download/mdsz6/')
```

## Check for NAs and NULLs
```{r}
#skim=skimr::skim(dataset)

sum(is.na(dataset))
sum(is.null(dataset))
```

## Level 1 
-	Let’s get familiar with our data. Create a table that shows how many times each state is represented in the dataset (variable name: Statecurrent)
-	One of our research questions is which subscales of the FACES are related to horizontal individualism? So let’s create the subscales we need to run the analyses

o	Create by COShindivid (Horizontal Individualism) doing COS1 + COS5 + COS9 + COS13

o	Create disengaged (FACEdisen) by FACES3 + FACES9 + FACES15 + FACES21 + FACES27 + FACES33 + FACES39

o	Create enmeshed (FACEenmesh) by  FACES4 + FACES10 + FACES16 + FACES22 + FACES28 + FACES34 + FACES40

o	Create Rigid (FACErigid) by  FACES5 + FACES11 + FACES17 + FACES23 + FACES29 + FACES35 + FACES41

o	Create Chaotic (FACEchaotic) by FACES6 + FACES12 + FACES18 + FACES24 + FACES30 + FACES36 + FACES42

o	Create Communication (FACEcomm) by FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52

o	Create Satisfaction (FACEsatis) by FACES53 + FACES54 + FACES55 + FACES56 + FACES57 + FACES58 + FACES59 + FACES60 + FACES61 + FACES62

```{r}
dataset1=dataset %>% 
  mutate(COShindivid=COS1 + COS5 + COS9 + COS13,
         FACEdisen= FACES3 + FACES9 + FACES15 + FACES21 + FACES27 + FACES33 + FACES39,
         FACEenmesh= FACES4 + FACES10 + FACES16 + FACES22 + FACES28 + FACES34 + FACES40,
         FACErigid= FACES5 + FACES11 + FACES17 + FACES23 + FACES29 + FACES35 + FACES41,
         FACEchaotic= FACES6 + FACES12 + FACES18 + FACES24 + FACES30 + FACES36 + FACES42,
         FACEcomm= FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52,
         FACEsatis= FACES53 + FACES54 + FACES55 + FACES56 + FACES57 + FACES58 + FACES59 + FACES60 + FACES61 + FACES62) %>% 
  select(COS1,COShindivid,FACEdisen,FACEenmesh,FACErigid,FACEchaotic,FACEcomm,FACEsatis,everything())
```

## Level 2
-	Provide the mean, standard deviation, median, and range of values for ‘FACEenmesh
-	Provide the mean, standard deviation, median, and range of values for ‘COShindivid’
-	Produce a visual that will show if the ‘FACEsatis’ variable contains any outliers. 

```{r}
library(purrr)

purr_list=data.frame(FACEenmesh=dataset1$FACEenmesh,COShindivid=dataset1$COShindivid)

desc_stat=function(x) {
  list(mean=mean(x,na.rm=T),sd=sd(x,na.rm=T),
       median=median(x,na.rm=T),range=range(x,na.rm=T))
}

stats=purr_list %>% 
  map(desc_stat) %>% 
  as.data.frame()

print(stats) #the mean, standard deviation, median, and range for FACEenmesh and COShindivid
```

```{r}
summary(dataset1$FACEsatis)

FACE=na.omit(dataset1$FACEsatis) %>% 
  data.frame() %>% 
  rename(face=1)

summary(FACE)

boxplot(FACE$face,main='Party Crashers or Trendsetters? A Tale of Two Data Points',xlab='FACEsatis',ylab='Count',lwd=1.5,boxfill='darkgreen',pch=1.5,outcol='red')
```

### ggplot2 version of the above
```{r}
library(ggplot2)

dataset1 %>%
  ggplot(aes(y=FACEsatis))+
  theme_bw()+
  geom_boxplot(fill='darkgreen',outlier.color = 'red',lwd=1.5,outlier.size = 2)+
  labs(title = 'Party Crashers or Trendsetters? A Tale of Two Data Points',x='FACEsatis',y='Count')+
  theme(plot.title = element_text(hjust = .5))
```

## Level 3
-	Does the ‘COShindivid’ variable meet the assumption of normality? Show both a visual and key statistics.


```{r}
summary(dataset1$COShindivid)

COSH=na.omit(dataset1$COShindivid) %>%
  data.frame()

summary(COSH)

hist(COSH$.,freq=F,main = 'Long Tail, Big Dreams: A Look at Our Left-Skewed Distribution',ylab = 'Density',xlab='COShindivid',col='darkgreen')
lines(density(COSH$.),lwd=2,col='red')

shapiro.test(COSH$.) #No, COShindivid violates normality
```

### ggplot2 version of the above
```{r}
#library(ggplot)

dataset1 %>%
  filter(!is.na(COShindivid)) %>% 
  ggplot(aes(x=COShindivid))+
  theme_bw()+
  geom_histogram(aes(y=..density..),col='black',fill='darkgreen',show.legend = F,bins=15)+
  geom_density(col='red',lwd=2)+
  labs(title = 'Long Tail, Big Dreams: A Look at Our Left-Skewed Distribution')+
  theme(plot.title = element_text(hjust = .5))
```

## Level 4
-	Create a correlation matrix to show the relationship between COShindivid, FACEdisen, FACEenmesh, FACErigid, FACEchaotic, FACEcomm, FACEsatis

```{r}
cor_data=dataset1[,c(2:8)]

cor_matrix=cor_data %>% 
  na.omit() %>% 
  cor() %>% 
  round(digits = 2) %>% 
  as.data.frame()

plot(cor_matrix)
```

### Heatmap for correlation matrix
```{r}
use_color=colorRampPalette(c('lightblue','darkblue'))

cor_matrix %>% 
  as.matrix() %>% 
  heatmap(margins = c(10,5),col=use_color(100),main = 'A Heatmap Exposé on Satisfaction and Communication')

```


```{r}
sessionInfo()
```

