---
title: "Psi Chi R Sponsored Workshop: Tiny Tasks in R (APS 2024)"
author: "Alan Lam"
#date: "`r Sys.Date()`"
date: "`r format(Sys.Date(), '%d %B %Y')`" 

output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: false
---

[**Source**: Psi Chi APS 2024](https://osf.io/c7adr/)

```{r setup,include=F}
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```

## Load packages and import data
```{r}
library(tidyverse)

dataset=read.csv('https://osf.io/download/pr4ws/')
```

## Check the data
```{r}
head(dataset)

#skimr::skim(dataset)
```

## Preparing the data

a.	Remove participants who are missing ‘Age’
```{r}
dataset1=dataset %>% 
  filter(!is.na(Age))

#sum(!complete.cases(dataset$Age))
```

b.	Remove participants who are missing ‘Gender’
```{r}
dataset2=dataset1 %>% 
  filter(!is.na(Gender))

#sum(!complete.cases(dataset1$Gender))
```

c.	Create the following variable ‘FACEenmesh’ which measures the extent to which a family is enmeshed, by summing the following items: FACES4, FACES10, FACES16,  FACES22, FACES28, FACES34, FACES40
```{r}
dataset3=dataset2 %>% 
  mutate(FACEenmesh = FACES4 + FACES10 + FACES16 + FACES22 + FACES28 + FACES34 + FACES40) %>% 
  select(FACEenmesh,everything())
```

d.	Identify participants with values considered outliers for ‘FACEenmesh’
```{r}
dataset3 %>% 
  ggplot(aes(x=FACEenmesh))+
  geom_boxplot()

dataset3 %>% 
  filter(!is.na(FACEenmesh)) %>% 
  summarise(mean(FACEenmesh),
            median(FACEenmesh),
            min(FACEenmesh),
            max(FACEenmesh),
            sd(FACEenmesh))

dataset3.5 = dataset3 %>% 
  filter(!is.na(FACEenmesh),
         FACEenmesh > 25)

dataset3.5
```

e.	Remove participants with values considered outliers on ‘FACEenmesh’
```{r}
dataset4 = dataset3 %>% 
  filter(!is.na(FACEenmesh),
         FACEenmesh < 25)

dataset4 %>% 
  ggplot(aes(x=FACEenmesh))+
  geom_boxplot()

dataset4 %>% 
  ggplot(aes(x=FACEenmesh))+
  geom_density()

```

##	Descriptives

a.	Find the mean of ‘FACEenmesh’
b.	Find the standard deviation of ‘FACEenmesh’
c.	Find the median of ‘FACEenmesh’
d.	Find the range of ‘FACEenmesh’
```{r}
dataset4 %>% 
  summarise(mean(FACEenmesh),
            sd(FACEenmesh),
            median(FACEenmesh),
            min(FACEenmesh),
            max(FACEenmesh),
            range(FACEenmesh))
```









