---
title: "Psi Chi R - Mar 2025"
#date: "`r Sys.Date()`"
output:
  html_document:
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---
Start Date: 7 Mar 2025

Report Date: `r format(Sys.Date(), '%d %B %Y')`

[Source: Psi Chi R](https://osf.io/vz3uj/wiki/home/)

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

#setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

rm(list=ls())

setwd("~/R/Psi_Chi_R")

library(tidyverse)

#total for bottom row
sum_rows = function(x) {
  x = as.data.frame(x)
  sums = sapply(x,function(col) if (is.numeric(col)) sum(col, na.rm = T) else NA)
  sums = as.data.frame(t(sums))
  names(sums) = names(x)
  rbind(x, sums)
}

## right column for total
sum_cols = function(x) {
  x$Total = rowSums(x[sapply(x, is.numeric)], na.rm = T)
  x
}

#dollar format function
dollars = function(x) {
  paste0("$",format(x,big.mark= ",",scientific=F))
}

desc_stats = function(x){
  c(min = min(x,na.rm=T),
    median = median(x,na.rm=T),
    max = max(x,na.rm=T),
    mean = mean(x,na.rm=T),
    sd = sd(x,na.rm=T))
}
```


## Clean and EDA
```{r}
data=read_csv('data.csv')

names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2) %>% 
  arrange(desc(Per_of_Missing))
```

## Level 1: Sort the data by GPA from low to high.

```{r}
data %>% 
  select(GPA,everything()) %>% 
  group_by(GPA) %>% 
  arrange(GPA) %>% 
  head()
```

## Level 2: Produce the means and standard deviations for the following variables:

GPA

Male_score (recognition for male psychologists like Sigmund Freud; higher scores = more recognition)

Female_score (recognition for psychologist women)

POC_score (recognition for psychologists of color)

White_score (recognition for white psychologists)

```{r}
var_list = c('GPA','Male_score','Female_score','POC_score','White_score')

var_res = list()

for (x in var_list){
  var_res[[x]] = desc_stats(data[[x]])
}

print(var_res)
```


## Level 3: Create a graph to compare the mean scores for recognition of women and for recognition of men.

```{r}
data=data %>% 
  select(Female_score,Male_score,everything())

#pivot longer to reshape DF for mean scores. See https://tidyr.tidyverse.org/reference/pivot_longer.html

data1=data %>% 
  pivot_longer(cols = c('Male_score','Female_score'),names_to = 'Gender_Recognition',values_to = 'Mean_Score') %>% 
  select(Gender_Recognition,Mean_Score,everything())

data1 %>% 
  ggplot(aes(x=Gender_Recognition,y=Mean_Score,fill = Gender_Recognition))+
  geom_col()+
  theme_bw()+
  labs(x=' ',y='Mean Score',title='"Who Gets the Kudos? An Average Look at Psychologist Recognition"', subtitle='Because Equality is Just a Suggestion.')+
  guides(fill = 'none')+
  theme(plot.title = element_text(hjust = .5),plot.subtitle = element_text(hjust = .5))
```


## Level 4: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable across male and female participants (Gender).

```{r}
t.test(data$Female_score,data$Gender)
```

Level 4 Bonus: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable between people who have completed a history of psychology course and people who have not taken a history of psychology course (Taken_history).

```{r}
data_no_hist = data %>% 
  select(Taken_history,Female_score,everything()) %>% 
  filter(is.na(Taken_history))

data_yes_hist = data %>% 
  select(Taken_history,Female_score,everything()) %>% 
  filter(!is.na(Taken_history))

#no statistical significance between the two groups
t.test(data_yes_hist$Female_score,data_no_hist$Female_score)
```

### Data set: 
```{r echo=F}
downloadthis::download_this(data,output_name = 'Mar2025_data',output_extension = '.xlsx')
```

```{r include=F}
#beep when done
if (require("beepr"))
  beepr::beep(2)
```