---
title: "Psi Chi R - May 2025"
#date: "`r Sys.Date()`"
output:
  html_document:
    lightbox: true
    theme: readable
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

Start Date: 3 May 2025

Report Date: `r format(Sys.Date(), '%d %B %Y')`

[Source: Psi Chi R](https://osf.io/2yhj3/wiki/home/)

In May 2024, Psi Chi R conducted a workshop at APS to help everyone learn R! That workshop was a success, and while we will not be at APS this year, we wanted to re-share that workshop as a resource for you! This month’s contest is a revamped version of what we covered in the workshop. I hope you enjoy! Enjoy the remainder of your semesters – summer is on the horizon!

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = T,message = F,warning = F)

#setwd("C:/Users/alanh/Documents/R/Psi_Chi_R")

rm(list=ls())

setwd("~/R/Psi_Chi_R")

library(tidyverse)

#total for bottom row
sum_rows = function(x) {
  x = as.data.frame(x)
  sums = sapply(x,function(col) if (is.numeric(col)) sum(col, na.rm = T) else NA)
  sums = as.data.frame(t(sums))
  names(sums) = names(x)
  rbind(x, sums)
}

## right column for total
sum_cols = function(x) {
  x$Total = rowSums(x[sapply(x, is.numeric)], na.rm = T)
  x
}

#dollar format function
dollars = function(x) {
  paste0("$",format(x,big.mark= ",",scientific=F))
}

desc_stats = function(x){
  c(min = min(x,na.rm=T),
    median = median(x,na.rm=T),
    max = max(x,na.rm=T),
    mean = mean(x,na.rm=T),
    sd = sd(x,na.rm=T))
}

#numeric notations
options(scipen=9999)
```

## Clean and EDA

```{r}
data=read_csv('data.csv')

names(data) = make.names(colnames(data))

SmartEDA::ExpData(data,type=2) %>% 
  arrange(desc(Per_of_Missing))
```

## Level 1: Preparing the data

```{r}
# 	Remove participants who are missing ‘Age’
# 	Remove participants who are missing ‘Gender’
data1= data %>% 
  filter(!is.na(Age),!is.na(Gender))
```

### Test your skills: Remove participants missing ‘Age’ and ‘Gender’ in one step, instead of two.

```{r}
# 	Create the following variable ‘FACEenmesh’ which measures the extent to which a family is enmeshed, by summing the following items: FACES4, FACES10, FACES16,  FACES22, FACES28, FACES34, FACES40

data2 = data1 %>% 
  mutate(FACEenmesh = FACES4+ FACES10+ FACES16+  FACES22+FACES28+ FACES34+FACES40) %>% 
  select(FACEenmesh,everything())
```


## Level 2: Data inspection + Descriptives

### Identify participants with values considered outliers for ‘FACEenmesh’. 

### Test your skills: Visualize outlier values for ‘FACEenmesh’.

#### Remove participants with values considered outliers on ‘FACEenmesh’; Find the mean of ‘FACEenmesh’; Find the standard deviation of ‘FACEenmesh’; Find the median of ‘FACEenmesh’; Find the range of ‘FACEenmesh’

```{r}
boxplot(data2$FACEenmesh)

data3 = data2 %>% 
  filter(FACEenmesh <= 25)
```

### Test your skills: Find the mean, standard deviation, median, and range of FACEenmesh in one step.

```{r}
#range is from 7 to 25
desc_stats(data3$FACEenmesh) %>% 
  print()
```

## Level 3: Inferential + Other Statistics

### Is there a statistically significant correlation between the number of siblings someone has and their enmeshment score?

No, there isn't.

```{r}
#No, there isn't a significant correlation.
data4 = data3 %>% 
  filter(!is.na(FACEenmesh) & !is.na(Siblings)) %>% 
  select(Siblings,everything())

cor.test(data4$FACEenmesh,data4$Siblings)

data4 %>% 
  ggplot(aes(y=FACEenmesh,x=Siblings))+
  geom_point()+
  geom_smooth()
```


### Test your skills: Is there a statistically significant difference in enmeshment between people who have siblings and those who do not? *Note, you may need to create a new variable to test this

```{r}
data5 = data4 %>% 
  mutate(have_siblings = case_when(Siblings > 0 ~ "YES",
                              TRUE ~ 'NO')) %>% 
  select(have_siblings,everything())

shapiro.test(data5$FACEenmesh[data5$have_siblings=='YES'])

shapiro.test(data5$FACEenmesh[data5$have_siblings=='NO'])

hist(data5$FACEenmesh[data5$have_siblings=='YES'])

hist(data5$FACEenmesh[data5$have_siblings=='NO'])

wilcox.test(data5$FACEenmesh~data5$have_siblings)
```

```{r}
#assumptions for Welch t-test

# data5$dev=with(data5, abs(FACEenmesh - ave(FACEenmesh, have_siblings, FUN = median)))
# 
# summary(aov(data5$dev ~data5$have_siblings))
# 
# t.test(data5$FACEenmesh~data5$have_siblings,var.equal = F)

```

## Level 4: Visualization

### Graph the relationship between the number of siblings someone has and their enmeshment score

```{r}
data5 %>% 
  ggplot(aes(y=FACEenmesh,x=Siblings))+
  theme_bw()+
  geom_point()+
  labs(title='Sibling Rivalry? More Like Sibling Enmeshment',subtitle='A Totally Scientific Look')+
  theme(plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))+
  geom_smooth()
```


### Test your skills: Visualize the difference in enmeshment between people who have siblings and those who do not

```{r}
data5 %>% 
  ggplot(aes(x=have_siblings,y=FACEenmesh,fill=have_siblings))+
  geom_col()+
  theme_bw()+
  labs(title='The "Only Child Sanctuary" vs. "Sibling Scrum": Enmeshment Edition',x='Have Siblings')+
  theme(plot.title = element_text(hjust = .5))+
  guides(fill ='none')
```


```{r include=F}
#beep when done
if (require("beepr"))
  beepr::beep(2)
```