---
title: "Psi Chi R - June 2024"
author: "Alan Lam"
#date: "`r Sys.Date()`"
date: "`r format(Sys.Date(), '%d %B %Y')`" 
output:
  html_document:
    always_allow_html: yes
    df_print: kable
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R](https://osf.io/3h4ge/)

## Load packages and import data

```{r}
#library(tidyverse)

library(dplyr)
library(purrr)

dataset=read.csv('https://osf.io/download/c3bfs/')
```

## Check the data

```{r}
head(dataset)

skimr::skim(dataset)
```

```{r}
# sum(is.na(dataset))
# 
# sum(is.null(dataset))
# 
# sum(!complete.cases(dataset))
```

## Level 1

Let’s get familiar with our data. Create a table that shows the frequency of each type of Pokémon in the dataset (variable name: type1). 

```{r}
tab1 = dataset %>% 
  filter(complete.cases(type1)) %>% 
  group_by(type1) %>% 
  count() %>% 
  arrange(desc(n))

tab1
```

Next, let’s look at the representation of each generation of Pokémon in the dataset. Create a table that shows the number of Pokémon in the dataset associated with each generation (variable name: generation)
```{r}
tab2 = dataset %>% 
  filter(complete.cases(generation)) %>% 
  group_by(generation) %>% 
  count() %>% 
  arrange(desc(n))

tab2
```


## Level 2-

Provide the mean, standard deviation, median, and range of values of attack stats (variable name: attack) for ‘Water’ type Pokémon (variable name: type1). 

```{r}
water_attack = dataset %>% 
  filter(type1 == 'Water',
         complete.cases(type1)) %>% 
  select(attack)

#create function for desc stats
desc_stat = function(x){
  c(mean = mean(x,na.rm = T),
  standard_dev = sd(x,na.rm = T),
  median = median(x,na.rm = T),
  range = range(x,na.rm = T))
}

map(water_attack,desc_stat)
#mean: 72.34
#std: 25.26
#median: 70
#range: 10 to 130
  
```

-Provide the mean, standard deviation, median, and range of values of speed stats (variable name: speed) for ‘Dragon’ type Pokémon (variable name: type1). 

```{r}
dragon_speed = dataset %>% 
  filter(type1 == 'Dragon',
         complete.cases(type1)) %>% 
  select(speed)

map(dragon_speed,desc_stat)
#mean: 80.19
#std: 24.62
#median: 82
#range: 40 to 142

```

## Level 3-

Are there any outliers for the ‘total’ stat? What is the value(s), and which Pokémon(s) is/are associated with it?
```{r}
library(ggplot2)

boxplot(dataset$total)

outlier_lower = dataset %>% 
  select(name,total) %>% 
  arrange(total)

outlier_upper = dataset %>% 
  select(name,total) %>% 
  arrange(desc(total))

#Wishwashi with a total of 175 is the lower outlier and Arceus with a total of 720 is the upper outlier.
```

##Level 4-

Is there a correlation between a Pokémon’s ‘total’ stat and their base level of experience? (variable: base_exp)


```{r}
dataset2=dataset %>% 
  filter(complete.cases(base_exp),
         complete.cases(total)) %>% 
  mutate(base_exp2=as.numeric(base_exp)) %>% 
  filter(!is.na(base_exp2),
         !is.na(total)) %>% 
  select(base_exp,base_exp2,total,everything())

#violates normality
shapiro.test(dataset2$base_exp2)
hist(dataset2$base_exp2)

# p-value < 2.2e-16, sample estimates: tau 0.9132707 
cor.test(dataset2$total,dataset2$base_exp2,method = 'kendall')

```


-Create a visualization that shows the average ‘total’ stat based on the primary type of the Pokémon (type1)
```{r}
dataset3 = dataset2 %>% 
  group_by('Pokemon Primary Type' =type1) %>% 
  summarise('Average of Total Stat'=round(mean(total),2)) %>% 
  arrange(desc(`Average of Total Stat`))

dataset3
```

```{r}
dataset3 %>% 
  ggplot(aes(y=`Pokemon Primary Type`,x=`Average of Total Stat`,fill=`Average of Total Stat`))+
  geom_col()+
  labs(x='Total Stat Average',y='Primary Type',
       title='A Bar Chart Brawl of Pokemon Power',
       subtitle='A look at Primary Types and their Average Total Stats',
       fill=' ')+
  theme_bw()+
  theme(plot.title = element_text(hjust=.5),
        plot.subtitle = element_text(hjust = .5))
```

