---
title: 'Psi Chi R Contest - Feb 2024'
author: 'By Alan Lam'
output:
  html_document:
    always_allow_html: yes
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: no
    anchor_sections: TRUE
    code_folding: hide
    code_download: true
---

[**Source**: Psi Chi R Contest](https://osf.io/mzkft/)


```{r setup,include=F}
knitr::opts_chunk$set(message=F,warning=F,echo = T)
```

```{r}
#Load packages and import data

#install.packages(tidyverse)

library(ggplot2)
library(dplyr)
library(readr)
library(tidyr)

feb=read.csv('feb2024_imdb_top_1000.csv')
```


## Level 1 -
To facilitate analyses, the ‘Runtime’ variable will need to be fixed so that ‘min’ is removed, and the column only contains numerical values. 
-To facilitate analyses, the ‘Genre’ variable will need to be edited so that each genre separated by a comma is listed in its own respective column.

```{r}
feb2=feb %>% 
  mutate(Genre =strsplit(Genre, ", ")) %>% 
  unnest_wider(Genre,names_sep = "_")

feb2$Runtime=gsub("min","",feb$Runtime) 


```


## Level 2-
Provide the mean, standard deviation, median, and range of values for ‘IMDB_Rating’

-Provide the mean, standard deviation, median, and range of values for ‘Gross’

```{r}
summary(feb2$IMDB_Rating)

mean(feb2$IMDB_Rating,na.rm = T) #Mean is 7.949
median(feb2$IMDB_Rating,na.rm = T) #Median is 7.9
sd(feb2$IMDB_Rating,na.rm = T) #Standard dev. is 0.275
range(feb2$IMDB_Rating,na.rm = T) #Range is 7.6 to 9.3

summary(feb2$Gross)

mean(feb2$Gross,na.rm = T) #Mean is $68,034,751
median(feb2$Gross,na.rm = T) #Median is $23,530,892
sd(feb2$Gross,na.rm = T) #Standard dev. is $109,750,043
range(feb2$Gross,na.rm = T) #Range is $1,305 to $936,662,225

```


## Level 3-
Provide the mean values for IMDB rating by Released Year-
What is the mean ‘IMDB_rating’ of Romance movies?

```{r}
IMDB_Rating_by_Year=feb2 %>% 
  group_by(Released_Year) %>% 
  summarise(Mean_Rating=mean(IMDB_Rating,na.rm = T))

print(IMDB_Rating_by_Year) #Results printed here

feb3=feb2 %>% 
  filter(Genre_1=='Romance' |
         Genre_2=='Romance' |
         Genre_3=='Romance')

mean(feb3$IMDB_Rating,na.rm = T) #Mean rating of Romance movies is 7.9256

```

## Level 4-
Create a plot that shows the average ‘IMDB_rating’ for Romance movies over time.
-Find the star who was lead in the most romance movies

```{r}

Romance_Plot=feb3%>% 
  mutate(Released_Year=as.numeric(Released_Year)) %>%
  group_by(Released_Year) %>% 
  summarise(Romance_Mean_Rating=mean(IMDB_Rating)) %>% 
  ggplot(aes(x=Released_Year,y=Romance_Mean_Rating))+
  geom_line(lwd=1,color='darkred') +
  labs(title='The Peaks and Valleys of Love in Romance Movies from 1920 to 2020',subtitle ='Looking at years with the highest and lowest average IMDB ratings',x='Release Years',y='Average IMDB Rating')+
  theme_bw()+
  theme(plot.title = element_text(hjust=.5),
        plot.subtitle = element_text(hjust = .5))+
  expand_limits(x=2025,y=7.5)

print(Romance_Plot) #Line plot on rating averages for romance movies

Romance_Lead=feb3 %>% 
  group_by(Lead_Star=Star1) %>% 
  summarise(Movie_Count=n()) %>% 
  arrange(-Movie_Count)

print(Romance_Lead) #Cary Grant
```

## Extra Stuff - not part of the submission

### Which the top ten directors with the highest average IMDB and Meta scores the most times
```{r}
library(forcats)

feb2.1=feb2 %>% 
  group_by(Director) %>% 
  filter(Released_Year>=2000) %>% 
  summarise(IMDB_Avg=mean(IMDB_Rating,na.rm = T),Meta_Avg=mean(Meta_score,na.rm = T),Headcount=n()) %>% 
  arrange(desc(Headcount),desc(IMDB_Avg),desc(Meta_Avg)) %>% 
  head(10) %>% 
  mutate(Headcount=as.numeric(Headcount))
```

```{r,fig.cap='Column Chart on Top 10 directors'}
feb2.1%>% 
  ggplot(aes(x=fct_reorder(Director,-Headcount),y=Headcount))+
  geom_col(fill='darkgreen')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 7),
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))+
  labs(y='Count',x='Directors',title='Top 10 Directors with the highest average IMDB and Meta ratings',subtitle = 'Looking at directors starting from year 2000 to now' )
```

## Aggregate count on genres 1-3
```{r}
feb3=feb2 %>% 
  mutate(Genre=paste(Genre_1,Genre_2,Genre_3,sep = ", ")) %>% 
  mutate(across(everything(), as.character)) %>% 
  pivot_longer(cols = c('Genre_1','Genre_2','Genre_3'),names_to = "Genre_column",values_to = "Genre_Aggregate") %>% 
  mutate(Gross=as.numeric(Gross),No_of_Votes=as.numeric(No_of_Votes))

feb4=feb3%>% 
  group_by(Genre_Aggregate) %>% 
  summarise(count=n())

feb4 %>% 
  na.omit() %>% 
  ggplot(aes(fill=count,y=fct_reorder(Genre_Aggregate,count),x=count)) +
  theme_bw()+
  geom_col()+
  labs(fill=' ',title = 'Supply and Demand, or Supply OR Demand?',subtitle = 'Looking at genres that gets the most, and the least, production',y='Genres',x='Production Count' )+
  expand_limits(x=800)+
  theme(plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))

```


